How has the Brazilian Amazon been constructed as a problem? An analysis of

### 2022-04-10 Draft_April_2022/Full_draft_20220401.rmd
#few changes to text #one new plot for exploration #comments on text for 4.3 in the google docs

---
title: How has the Brazilian Amazon been constructed as a problem? An analysis of
  presidential speeches since 1985
author:
- Livio Silva-Muller^[Phd Candidate, The Geneva Graduate Institute , livio.silva@graduateinstitute.ch]
- Henrique Sposito^[Phd Candidate, The Geneva Graduate Institute Geneva, henrique.sposito@graduateinstitute.ch]
date: "April 2022"
output:
  word_document:
    reference_docx: template.docx
  pdf_document: default
  html_document:
    df_print: paged
bibliography: references.bib
csl: chicago.csl
abstract: This paper ...
---

@@

[^2]: The reasoning here is that knowledge of high or low deforestation rates might drive presidents to speak about the Amazon. Matching deforestation with speech dates is a complicated endeavor. INPE published consolidated deforestation data with almost two years of delay until 2005 [@capobianco2021, pp. 60]. Preliminary data was published earlier, but with lower degrees of confidence in the findings. For the subsequent years, the consolidated figures for a given year tend to come out in August of the subsequent year. However, it also seems to be the case that the executive government have access to the data before everyone else. In addition, other sources indicating if deforestation is going up or down, as fire data or lower resolution deforestation data (DETER for example), circulates within the same year. The year of 1988 is particularly indicative of these complications: a report dating 1988 was circulating with deforestation and fire figures[@fearnside1990], and a New York Times article about the issue was written with comments by an INPE scientist [@simons1988]. Hence, we believe the most appropriate way of matching is without any lags on deforestation.

@@

Table 2, below, displays the multinational regression coefficients for the correlation between diverse problem constructions and locations. The regression coefficients express the relative probability in relation to the reference categories, which are Amazonian states for location and environmental conservation for problem construction. Although all the other mixed types problem-constructions were included in the model, we choose to display and focus the analysis on the pure types. From the outset, we notice that problem constructions of pure economic integration and pure social development correlate in negative statistically significant ways to both international settings and Brasilia in relation to environmental conservation problem constructions in Amazonian states. These findings indicate that constructing the Amazon as an issue of  environmental conservation is more likely to happen in international settings and in Brasilia than in Amazonian states. Additionally, pure sovereignty correlates in negative statistically significant ways to international settings in relation to conservation in Amazonian states. That is, constructing the Amazon as an issue of sovereignty is less likely in international settings than it is in Amazonian States. Interestingly, we see no statistically significant correlations between problem constructions in non-Amazonian states in relation to Amazonian states. This indicates that when presidents speak about the Amazon at the state level, constructions might be rather similar across different states. Furthermore, we also notice that some of the control variables correlate with some Amazonian problem constructions in interesting ways. For example, pure sovereignty constructions correlate negatively with election years in relation to conservation. That is, in election years conservation constructions are more likely to take place in comparison to sovereignty. As well, annual deforestation rates correlate positively with economic integration constructions in relation to conservation. This indicates that both deforestation increases and presidents are also more likely to construct the Amazon as an issue of economic integration.

>>>>

---
title: How has the Brazilian Amazon been constructed as a problem? An analysis of
  presidential speeches since 1985
author:
- Livio Silva-Muller^[Phd Candidate, The Geneva Graduate Institute , livio.silva@graduateinstitute.ch]
- Henrique Sposito^[Phd Candidate, The Geneva Graduate Institute Geneva, henrique.sposito@graduateinstitute.ch]
date: "April 2022"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document:
    reference_docx: template.docx
bibliography: references.bib
csl: chicago.csl
abstract: This paper ...
---

@@

[^2]: The reasoning here is that knowledge of high or low deforestation rates might drive presidents to speak about the Amazon. Nevertheless, matching deforestation with speech dates is a complicated endeavor. INPE published consolidated deforestation data with almost two years of delay until 2005 [@capobianco2021, pp. 60]. Preliminary data was published earlier, but with lower degrees of confidence in the findings. For the subsequent years, the consolidated figures for a given year came out in August of the subsequent year. However, it also seems to be the case that the executive government have access to the data before everyone else. In addition, other sources indicating if deforestation is going up or down, as fire data or lower resolution deforestation data (DETER for example), or even other sources, circulated within the year the data covered. The year of 1988 is particularly indicative of these complications: a report dating 1988 was circulating with deforestation and fire figures[@fearnside1990], and a New York Times article about the issue with deforestation rates for 1988 was written with comments by an INPE scientist [@simons1988]. Hence, we believe the most appropriate way of matching is without any lags on deforestation.

@@

```{r Figure 5: pure types in time by location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}

pure_types_time_location <- ama_mx %>%
  count(president, mx_cat2, mx_cat, year, location_cat) %>%
  group_by(president, year) %>%
  mutate(perc = n / sum(n)) %>% 
  filter(mx_cat2 == "Pure-types") %>%
  filter(location_cat != "Non Identified") %>%
  ggplot(aes(x=as.numeric(year), y=perc, color=mx_cat)) +
  geom_smooth(aes(color=mx_cat), se=FALSE, size=.5) +
  scale_y_continuous(labels = percent_format(accuracy=1)) +
  labs(x = "", y = "", title ="Share of each pure type in time by location",
       subtitle = "Sample composed by 1885 Amazonian statements in presidential speeches since 1985",
       caption = "") +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "bottom")+
  facet_wrap(~location_cat, scales= "free_y", ncol=2)

pure_types_time_location

Table 2, below, displays the multinomial regression coefficients for the correlation between problem constructions and locations. The regression coefficients express the relative probability in relation to the reference categories, which are Amazonian states for location and environmental conservation for problem construction. Although all the other mixed types problem-constructions were included in the model, we choose to display and focus the analysis on the pure types. From the outset, we notice that problem constructions of pure economic integration and pure social development correlate in negative statistically significant ways to both international settings and Brasilia in relation to environmental conservation problem constructions in Amazonian states. These findings indicate that constructing the Amazon as an issue of  environmental conservation is more likely to happen in international settings and in Brasilia than in Amazonian states. Additionally, pure sovereignty correlates in negative statistically significant ways to international settings in relation to conservation in Amazonian states. That is, constructing the Amazon as an issue of sovereignty is less likely in international settings than it is in Amazonian States. Interestingly, we see no statistically significant correlations between problem constructions in non-Amazonian states in relation to Amazonian states. This indicates that when presidents speak about the Amazon at the state level, constructions might be rather similar across different states. Furthermore, we also notice that some of the control variables correlate with some Amazonian problem constructions in interesting ways. For example, pure sovereignty constructions correlate negatively with election years in relation to conservation. That is, in election years conservation constructions are more likely to take place in comparison to sovereignty. As well, annual deforestation rates correlate positively with economic integration constructions in relation to conservation. This indicates that both deforestation increases and presidents are also more likely to construct the Amazon as an issue of economic integration.
